Mining Scenario/Transaction Pairs in HW/SW Co-verification Using Symbolic Execution

### 2017-04-06 paper.tex
comment
comments, minor

subsequent section, we describe each step in details.\\ 

@@

semantics. The software netlist model is cycle-accurate as well as 

@@

in Verilog such as procedural blocks and continuous assignments, multiple always
blocks, multiple modules and translates them into an equivalent C program.  This

@@

models from RTL description, mainly targeted for word-level formal hardware 

@@

satisfaction~\cite{leo-thesis}.  To the best of our knowledge, this is the first 
attempt to demonstrate the efficacy of such translation in the context of 

@@

Here, $\mathit{In}$, $\mathit{Out}$, $\mathit{Seq}$, $\mathit{Comb}$
are programs variables that model \emph{input}, \emph{output}, 

@@

Verilog RTL circuit containing an always block and continuous
assignment statement and the equivalent software netlist in C.

>>>>

subsequent section, we describe each step in detail.\\ 

@@

semantics \sjcmt{ref for synthesis semantics?}. The software netlist model is cycle-accurate as well as 

@@

in Verilog such as procedural blocks and continuous assignments, multiple {\em always}
blocks, multiple modules, and translates them into an equivalent \sjcmt{we should specify equivalent in what sense} C program.  This

@@

models from RTL description, primarily targeted for word-level formal hardware 

@@

satisfaction\sjcmt{?}~\cite{leo-thesis}.  To the best of our knowledge, this is the first 
attempt to demonstrate the efficacy of such a translation in the context of 

@@

Here, $\mathit{In}$ \sjcmt{this is missing from the def}, $\mathit{Out}$, $\mathit{Seq}$, $\mathit{Comb}$
are program variables that model \emph{input}, \emph{output}, 

@@

Verilog RTL circuit containing an {\em always} block and continuous
assignment statements, and the equivalent software netlist in C.
